---
title: "Case Study for Seedstar"
author: "Rodrigo Taira"
date: "6 December 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



## Introduction 
- This is a presentation of a task given as an assignment for the Seedstar Data Scientist Internship Position.
- To implement this case, it was used R programming language as main tool for data analysis. 
- Most part of the graphs were implemented using ggplot2 library. 

## Problem Assignment and Questions

- A dataset was provided by this link: https://docs.google.com/spreadsheets/d/1YT0-PTttD-k1y8KHXwfHm5rkfOucIj-eGLvSiFOCchY/edit#gid=0
- In a brief view,  it can be perceived that the data provided is about loans status from customers.  
- It was asked to analyze this dataset and create a model to predict the 'label' index. That has just two possible values either '0' and '1'.  
- Some of the details that were very useful to get some insights were Education_Status, Gender, No_Children and Amount.
- How the Label Status is distributed considering Education Status, Reason, Number of Children and etc? 

## Acquire Data 

- First step was to retrieve the data from the link with the gsheet library. 
- After a quick look, I got the summary of the data to check all the data types.
- It was organised the data types of each column and check which type suits better to the context for a better analysis of the data.

```{r }
library(gsheet)
dataset <- gsheet2tbl('https://docs.google.com/spreadsheets/d/1YT0-PTttD-k1y8KHXwfHm5rkfOucIj-eGLvSiFOCchY/edit#gid=0')
dataset$Education_Status <- as.factor(dataset$Education_Status)
dataset$Amount <- as.numeric(dataset$Amount)
dataset$Gender <- as.factor(dataset$Gender)
dataset$Reason <- as.factor(dataset$Reason)
dataset$label <- as.factor(dataset$label)
dataset$Reason <- as.factor(dataset$Reason)
dataset$referrals <- as.factor(dataset$referrals)
dataset$Name <- as.character(dataset$Name)
dataset$No_Children <- as.factor(dataset$No_Children)
dataset_no_na <- na.omit(dataset)
dataset_with_na <- dataset[!complete.cases(dataset),]

dataset[!complete.cases(dataset),]
table(is.na(dataset))
colSums(is.na(dataset))
```

## 
- Plot to check how the 'label' is distributed among the Customers. 

```{r}

barplot(table(dataset$label), xlab = "Label", ylab = "Total of Customers", main = "Barplot of the Total Customers per Label")
```

## Process of the data for analysis
- The probability of label be '1' is higher for females with better education. 
```{r}
library(tidyverse)
ggplot(dataset, aes(x = Education_Status, fill = factor(label))) + facet_wrap(~Gender) +  stat_count(width = 0.5) + xlab("Education Status") + ylab("Total of Customers") + labs(fill="label") + ggtitle('Barplot of the Total of Customers per Education Status by Gender')
```

##
- The probability of label be '1' is higher for females with less or no Children. 

```{r}
ggplot(dataset, aes(x = No_Children, fill = label)) + geom_bar() + facet_wrap(~Gender) + xlab("Number of Children") + ylab("Total of Customers") + ggtitle('Barplot of the Total Customers per number of children by Gender')

ggplot(dataset, aes(x = Reason, fill = label)) + geom_bar() + facet_wrap(~Gender) + xlab("Reason") + ylab("Total of Customers") + ggtitle('Barplot of the Total Customers per Reason by Gender')
```

## 
- It is perceved that the median of the loan amount of the males with label equal '0' is almost 150
```{r}

ggplot(dataset, aes(x = label, y = Amount)) + geom_boxplot() + ggtitle("Boxplot of the Amount per Label Status by Gender") + facet_wrap(~Gender) + scale_y_continuous(limits = c(0,250)) 
```
## 

```{r}

ggplot(data = dataset) + 
  geom_point(mapping = aes(x = Age, y = Amount, color = label)) + ylim(c(0, 300)) + ggtitle("Amount per Age by Label")

```

## Prediction Model 

```{r}

library(randomForest)
library(caTools)

str(dataset)
dim(dataset)
apply(dataset, 2, function(x) length(unique(x)))

##set.seed(123)
ind <- sample.split( Y = dataset$label, SplitRatio = 0.8)
train_dataset <- dataset[ind,]
test_dataset <- dataset[!ind,]
train_dataset$Age <- na.roughfix(train_dataset$Age)
train_dataset$Name <- NULL
train_dataset$loan_ident <-NULL
train_dataset$Campaign <-NULL
train_dataset <- na.omit(train_dataset)
cleandata <- dataset[complete.cases(dataset),]


train_dataset$Campaign <- NULL


## Fitting the model 
colSums(is.na(train_dataset))
modelRandom <- randomForest(label~ Gender, data = train_dataset, importance=TRUE, proximity=TRUE)
modelRandom
importance(modelRandom)

library(pROC)

PredictionsWithProbs <- predict(modelRandom, test_dataset, type = 'prob')
auc <- auc(test_dataset$label, PredictionsWithProbs[,2])
plot(roc(test_dataset$label, PredictionsWithProbs[,2]), main = 'ROC Curve',ylab ='True positive rate' ,xlab = 'False positive rate')

```

## Prediction
```{r}

PredictionsWithClass <- predict(modelRandom, test_dataset, type = 'class')
t <- table(predictions = PredictionsWithClass, actual = test_dataset$label)
t

## Accuracy metric

sum(diag(t)/sum(t))



```